Meta-analysis of the Interoceptive Accuracy Scale

### 2024-02-28 analysis/study1.qmd
sample tabs
Think its just this?

@@

@@

>>>>

efa4 <- parameters::factor_analysis(data2, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

display(efa4)

```

efa4 <- parameters::factor_analysis(data3, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

#### sample 4

efa4 <- parameters::factor_analysis(data4, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

efa4 <- parameters::factor_analysis(data5, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

efa4 <- parameters::factor_analysis(data5, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

efa4 <- parameters::factor_analysis(data6, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

efa4 <- parameters::factor_analysis(data7a, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

efa4 <- parameters::factor_analysis(data7b, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

efa4 <- parameters::factor_analysis(data7c, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

efa4 <- parameters::factor_analysis(data8a, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

efa4 <- parameters::factor_analysis(data8b, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

efa4 <- parameters::factor_analysis(data9, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

efa4 <- parameters::factor_analysis(data10a, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

efa4 <- parameters::factor_analysis(data10b, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

display(compare_mods(data1b))

```

display(compare_mods(data2))

```

display(compare_mods(data3))

```

display(compare_mods(data4))

```

display(compare_mods(data5))

```

display(compare_mods(data6))
```

display(compare_mods(data7a))
```

display(compare_mods(data7b))

```

display(compare_mods(data7c))

```

display(compare_mods(data8a))
```

display(compare_mods(data8b))
```

display(compare_mods(data9))

```

display(compare_mods(data10a))

```

display(compare_mods(data10b))

```

@@

```{r}
display(compare_mods_h(data1b))
```

```{r}
display(compare_mods_h(data2))
```

```{r}
display(compare_mods_h(data3))
```

```{r}
display(compare_mods_h(data4))
```

```{r}
display(compare_mods_h(data5))
```

```{r}
display(compare_mods_h(data6))
```

```{r}
display(compare_mods_h(data7a))
```

```{r}
display(compare_mods_h(data7b))
```

```{r}
display(compare_mods_h(data7c))
```

```{r}
display(compare_mods_h(data8a))
```

```{r}
display(compare_mods_h(data8b))
```

```{r}
display(compare_mods_h(data9))
```

```{r}
display(compare_mods_h(data10a))
```

```{r}
display(compare_mods_h(data10b))
```
